\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/figures.tex
figures pass

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-overview.png}
    \caption{\textbf{\scheme Operations}\,---\,%
      \TODO{Caption}
    }
    \label{fig:overview}
\end{figure}
}

@@

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
            %Multicore Implementation  &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,}
    \label{tab:compare}
\end{table*}
}

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
    \caption{\textbf{Station Architecture}\,---\,%
      \TODO{Caption}
    }
    \label{fig:implementation}
\end{figure}
}

>>>>

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-overview.png}
    \caption{\textbf{\scheme Operations}\,---\,%
        Clients first register by sending a secret seed in a steganographic tag past the station in a
        normal TLS connection to a Decoy site. Clients then connect to an address derived from the seed,
        which the station responds as a phantom host. If the client can prove knowledge of the
        seed used during registration, they are allowed access to the proxy. Otherwise,
        their traffic is forwarded to a Mask Site to make it difficult for censors to distinguish
        phantom hosts from legitimate ones.
    }
    \label{fig:overview}
\end{figure}
}

@@

\newcommand{\TabCompare}{
\begin{table*}[t]
    \centering
    \begin{tabular}{l|cccccccc}
            % Multiflow? Waterfall?
            & \rot{Telex~\cite{telex11}} &
            \rot{Cirripede~\cite{cirripede11}} &
            \rot{Decoy Routing~\cite{curveball11}} &
            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
            \hline
                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
            Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
            %Multicore Implementation  &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
    \end{tabular}
    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,
        ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
        without needing an inline element in the ISP network.
        ``Handles asymmetric routes'' refers to schemes that work when only one direction (either client to decoy or decoy to server) is seen by the station.
        ``Replay attacks'' refers to censors who may replay/preplay previous messages or actively probe
        the protocol.
        ``Traffic analysis'' includes latency, inter-packet timing, and website fingerprinting.
        ``Unlimited Sessions'' shows schemes that do not need to repeatedly reconnect to download
        or upload arbitrarily large content.}
    \label{tab:compare}
\end{table*}
}

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
    \caption{\textbf{Station Architecture}\,---\,%
        We used PF\_RING to receive packets from a 10~Gbps packet tap, which we load balance
        across 4~CPU cores. The detector process identifies and processes registrations, and forwards
        packets destined to registered dark decoy addreses to a local application. The application
        determines if the client is legitimate (using a seed shared during registration) and forwards
        their traffic to a proxy. Otherwise, the application responds as if it were the mask site.
    }
    \label{fig:implementation}
\end{figure}
}
